How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-06-14 paper.tex
cleanup repo
a few little updates

\newcommand{\versionnumber}{0.1}  % you should update the minor version number in preprints and major version number of submissions.
\newcommand{\githubrepository}{\url{https://github.com/GrossfieldLab/article_templates}}

@@

In all of these cases, it is necessary to interact with the folks who develop
and support the code. How you go about it has an enormous impact on your
likelihood of success and how you are viewed, but this is not something that is
explicitly taught in most places.  {\emph The goal of this work is to reveal the hidden
curriculum -- what's expected of a software consumer, how to ask for help, how
to contribute productively to a software community (regardless of whether you
can write code).}

@@

\section{Prerequisites}

Training articles should clearly state the target audience and knowledge prerequisites.
Key prerequisites should be noted in the article abstract to permit readers to rapidly ascertain an articles suitability.

\subsection{Background knowledge}

Although the authors may imagine a particular career-level (e.g., undergraduate or graduate), given the diversity of disciplinary curricula, it is more important to specify precisely any knowledge prerequisites (e.g., vector calculus, basic thermodynamics).

\subsection{Software/system requirements}

If a particular software or programming environment plays a central role in the article, that should be specified.

\section{Content and links}

A training article may on additional files and materials; clearly indicate where and how these are available, with links, and how they are being archived for the long-term and maintained so they stay current.
You will likely want to reference your GitHub repository as a central point to access all of this information, and then the GitHub repository may link out to other content as needed.

>>>>

\newcommand{\versionnumber}{0.1}  % you should update the minor version number in preprints and major version number of submissions.
\newcommand{\githubrepository}{\url{https://github.com/GrossfieldLab/software_community}}

@@

In all of these cases, it is necessary to interact with the people who develop
and support the code. How you go about it has an enormous impact on your
likelihood of success and how you are viewed, but this is not something that is
explicitly taught in most places.  {\emph The goal of this paper is to reveal
the hidden curriculum -- what's expected of a software consumer, how to ask for
help, how to contribute productively to a software community (regardless of
whether you can write code).}

Asking strangers for help can be intimidating, regardless of your

@@

emphasize the idea of a social contract: what do developers owe the users, what
do users owe developers, what do users owe other users

connect to open science: FAIR principles say developers should want code to be
reusable. Publishing the code isn't enough, you need to make it usable as well.
That means support.

\section{Target Audience}

This paper is primarily aimed at junior scientists who are new to performing
research and inexperienced at asking for help. However, we hope it will be
valuable to anyone who uses software to do their research and struggles to ask
for help.
